### 2015-11-06 CVPR16/Source/experiments.tex
changes

In this section, we first benchmark our continuous occlusion model for point-to-object association against the baseline method using detection bounding boxes and state-of-the-art methods for motion segmentation \cite{Rao_etal_2010,Brox_Malik_2010}. We then show how the proposed model benefits the task of 3D localization in autonomous driving. For our experiments, we use the KITTI dataset~\cite{geiger2013vision}, which consists of video sequences of road scenes under a variety of driving conditions including highways and residential areas. It also provides ground truth data for different tasks such as segmentation, detection, tracking and 3D localization.

>>>>

In this section, we first benchmark our continuous occlusion model for point-to-object association against the baseline method using detection bounding boxes and state-of-the-art methods for motion segmentation \cite{Rao_etal_2010,Brox_Malik_2010}. We then show how the proposed model may be applied for 3D localization in road scenes. For our experiments, we use the KITTI dataset~\cite{geiger2013vision}, which consists of video sequences of road scenes under a variety of driving conditions. 
%It also provides ground truth data for different tasks such as segmentation, detection, tracking and 3D localization.

### 2015-11-06 CVPR16/Source/experiments2.tex
changes

\section{Experimental results}
\label{sec:experiments}

In this section, we first benchmark our continuous occlusion model for point-to-object association against a baseline method that uses detection bounding boxes and state-of-the-art methods for motion segmentation. We then show how the proposed model benefits the task of 3D localization in autonomous driving. For our experiments, we use the KITTI dataset~\cite{geiger2013vision}, which consists of video sequences of road scenes under a variety of driving conditions including highways and residential areas. It also provides ground truth data for different tasks such as segmentation, detection, tracking and 3D localization.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Association experiment}

We first perform the association experiment that compares the accuracy of point-to-object association using the proposed model against those of the detection bounding box baseline method (BBox) and state-of-the-art motion segmentation methods, namely robust algebraic segmentation with hybrid perspective constraints (RAS)~\cite{Rao_etal_2010} and spectral clustering with point track spatial affinity (BM)~\cite{Brox_Malik_2010}.

@@

\subsubsection{Association results}

For each sequence of the KITTI dataset, the methods of \cite{Felzenszwalb_etal_2010} and \cite{Choi_Savarese_2010} are used respectively for computing detection bounding boxes and object tracklets. We then apply \cite{Zach2007} on object tracklets to extract point tracks. From these point tracks, we create four different sets of input point tracks, namely all point tracks, occluded point tracks, dynamic point tracks and dynamic and occluded point tracks, to examine various aspects of the methods (our method focuses on occlusion scenes while RAS and BM favour dynamic scenes). In addition to point tracks, the parameters of all TPs estimated by the method~\cite{Song_Chandraker_2014} are provided to our method (for computing association probability) and the baseline method (for depth ordering).

Figure~\ref{fig:assoc-occ-results} shows the association errors --- the percentages of point tracks incorrectly assigned to objects --- of all methods on four sets of input point tracks for each sequence of the KITTI dataset, while the mean results over all sequences are presented in Table~\ref{tab:meanAssoc}. From Figure~\ref{fig:assoc-occ-results}, our method is usually the most accurate among all methods, leading to the best mean errors on all sets of input point tracks in Table~\ref{tab:meanAssoc}, which is followed by the bounding box baseline method. This clearly shows the advantage of our continuous occlusion model over the simple baseline method for resolving occlusions. RAS and BM often have the highest errors in Figure~\ref{fig:assoc-occ-results}, and hence the highest mean errors on all sets of input point tracks in Table~\ref{tab:meanAssoc}.

More importantly, both RAS and BM rely on motions of objects for clustering point tracks, therefore they cannot work well with static point tracks (e.g., point tracks belong to parked cars). This fact can be observed in Table~\ref{tab:meanAssoc}, where there are large differences in the mean errors of both methods on data containing static point tracks (i.e., rows 2 and 4) and data consisting of dynamic point tracks only (i.e., rows 1 and 3). In contrast, our method and the baseline method are relatively independent of object motions, resulting in smaller performance gaps.

@@

\newlength{\tblimgwidth}
\setlength{\tblimgwidth}{0.40\textwidth}
\begin{table*}
  \centering
  \begin{tabular}{ccc}
    & Associations & Error in association\\
    \rotatebox{90}{\hspace{2em} BBox} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_bbox2D_model-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} BM} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} RAS} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_RAS-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_RAS_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} Ours} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_contPtTracks-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_contPtTracks_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} BBox} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_bbox2D_model-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} BM} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} RAS} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_RAS-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_RAS_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} Ours} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_contPtTracks-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_contPtTracks_correct_incorrect-small.png}
  \end{tabular}
  \caption{Qualitative results of the association experiment. The left column
  shows the point track assignments to appropriate objects. Each color represents
a different object to which point tracks can be associated to. Right column shows the
probabilistic error in association: low error points are in blue while high error points are in red.
Note that our method changes smoothly at the object boundaries with
intermediate probabilities, while the baseline method has merely 0-1 error.} 
\end{table*}

>>>>

\section{Experiments}
\label{sec:experiments}

In this section, we benchmark our continuous occlusion model for point-to-object association against the baseline method using detection bounding boxes and state-of-the-art methods for motion segmentation \cite{Rao_etal_2010,Brox_Malik_2010}. We then show how the proposed model may be applied for 3D localization in road scenes. For our experiments, we use the KITTI dataset~\cite{geiger2013vision}, which consists of video sequences of road scenes under a variety of driving conditions. 
%It also provides ground truth data for different tasks such as segmentation, detection, tracking and 3D localization.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Association Experiments}

\vspace{-0.4cm}
\paragraph{Setup}

We first perform the association experiment that compares the accuracy of point-to-object association using our proposed model against a heuristic baseline and state-of-the-art motion segmentation methods. The detection bounding box baseline method (BBox) is as described at the end of Section \ref{sec:association}. For motion segmentation, we use robust algebraic segmentation with hybrid perspective constraints (RAS)~\cite{Rao_etal_2010} and spectral clustering with point track spatial affinity (BM)~\cite{Brox_Malik_2010}.

@@

For each sequence of the KITTI dataset, the methods of \cite{Felzenszwalb_etal_2010} and \cite{Choi_Savarese_2010} are used for computing detection bounding boxes and object tracklets, respectively. We then apply \cite{Zach2007} to extract point tracks. Note that our method can handle occlusions in both static and dynamic scenes, but motion segmentation focuses on dynamic scenes. For a complete evaluation, we create organize the point tracks into four sets: all point tracks, occluded point tracks, dynamic point tracks and dynamic as well as occluded point tracks. In addition to point tracks, the parameters of all objects (cars) estimated by the method of \cite{Song_Chandraker_2014} are provided to our method (for computing association probability) and the baseline BBox method (for depth ordering).

\vspace{-0.4cm}
\paragraph{Results}
Figure~\ref{fig:assoc-occ-results} shows the association errors -- the percentages of point tracks incorrectly assigned to objects -- for all methods on the four sets of input point tracks, for each sequence of the KITTI dataset. The mean results over all sequences are summarized in Table~\ref{tab:meanAssoc}. From Figure~\ref{fig:assoc-occ-results}, our method is usually the most accurate among all methods, leading to the best mean error on all sets of input point tracks in Table~\ref{tab:meanAssoc}, which is followed by the bounding box baseline method. This clearly shows the advantage of our continuous occlusion model over the simple baseline method for resolving occlusions. RAS and BM often have the highest errors in Figure~\ref{fig:assoc-occ-results}, thus, the highest mean errors on all sets of input point tracks in Table~\ref{tab:meanAssoc}.

More importantly, both RAS and BM rely on motions of objects for clustering point tracks, therefore they cannot work well with static point tracks (for example, point tracks that belong to parked cars). This fact can be observed in Table~\ref{tab:meanAssoc}, where there are large differences in the mean errors of both methods on data containing static point tracks (rows 2 and 4) and data consisting of dynamic point tracks only (rows 1 and 3). In contrast, our method and the baseline method are relatively independent of object motions, resulting in smaller performance gaps. Further, our method also outperforms motion segmentation on dynamic objects (row 3), which shows the effect of detection bounding boxes and by a more significant margin when occlusions are present (row 1), which shows the effect of our occlusion modeling.

Qualitative comparisons of point track associations from various methods are shown in Figure \ref{fig:qualitative}. We note the low errors using our occlusion model and the smooth transition of assignment across object boundaries.

@@

\newlength{\tblimgwidth}
\setlength{\tblimgwidth}{0.40\textwidth}
\begin{figure*}
  \centering
  \begin{tabular}{ccc}
    & Associations & Error in association\\
    \rotatebox{90}{\hspace{2em} BBox} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_bbox2D_model-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} BM} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} RAS} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_RAS-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_RAS_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} Ours} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_contPtTracks-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_contPtTracks_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} BBox} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_bbox2D_model-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} BM} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} RAS} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_RAS-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_RAS_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} Ours} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_contPtTracks-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_contPtTracks_correct_incorrect-small.png}
  \end{tabular}
  \caption{\small Qualitative results of the association experiment. The left column
  shows the point track assignments to appropriate objects. Each color represents
a different object to which point tracks can be associated to. Right column shows the
probabilistic error in association: low error points are in blue while high error points are in red.
Note that our method changes smoothly at the object boundaries with
intermediate probabilities, while the baseline method has merely 0-1 error.}
\label{fig:qualitative}
\end{figure*}
